### 2024-02-14 documentation/thesis/thesis_document.tex
.

\hypertarget{sensor-characterisation-noise}{%
\subsection{Sensor Characterisation:
Noise}\label{sensor-characterisation-noise}}

@@

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external field
interference.

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of N=10000 measured values was recorded for the baseline
measurement.

The output signal of the sensor is then continuously measured and
recorded. It is important to carry out the measurement over a
sufficiently long period of time in order to record both short-term and
long-term fluctuations. For this purpose, N=2000 further measured values
were taken with a trigger and readout rate of one measurement per
second.

In order to quantify the noise, the standard deviation or the mean
square deviation of the signal is calculated. These parameters provide
information about the variation of the signal over time and therefore
about the sensor background noise.

\begin{longtable}[]{@{}lll@{}}
\caption{Sensor noise evaluation result used symbols
\label{Sensor_noise_evaluation_result_used_symbols.csv}}\tabularnewline
\toprule
Symbol & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & Unit & Description\tabularnewline
\midrule
\endhead
\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
\(\mu_{t}\) & \(\mu\)T &\tabularnewline
\(\mu_{nl}\) & \% &\tabularnewline
\(\sigma_{nl}\) & \% &\tabularnewline
\bottomrule
\end{longtable}

@@

@@

\hypertarget{temperature-sensitivity}{%
\subsection{Temperature Sensitivity}\label{temperature-sensitivity}}

@@

using same setup as in read noise but with programmed temperature
controller of the chamber

\hypertarget{linearity}{%
\subsection{Linearity}\label{linearity}}

@@

\hypertarget{result-analysis-1}{%
\subsubsection{Result Analysis}\label{result-analysis-1}}

@@

>>>>

\hypertarget{sensor-characterisation-background-noise}{%
\section{Sensor Characterisation:
Background-Noise}\label{sensor-characterisation-background-noise}}

@@

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external field
interference. The temperature chamber for all noise tests is set to
\emph{20°C}.

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values was recorded for the baseline
measurement.

The output signal of the sensor is then continuously measured and
recorded. It is important to carry out the measurement over a
sufficiently long period of time in order to record both short-term and
long-term fluctuations. For this purpose, \emph{N=2000} further measured
values were taken with a trigger and readout rate of one measurement per
second.

In order to quantify the noise, the standard deviation of the signal is
calculated. These parameters provide information about the variation of
the signal over time and therefore about the sensor background noise.

@@

The following figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
shows the measured values of these sensors. In the following, these are
analysed for each sensor examined.

The following data is shown in the plots:

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Background noise level with reference to the baseline
\item
  Histogram of the background noise level
\end{itemize}

\%\%Sensor\_noise\_evaluation\_results.csv\%\%

\hypertarget{sensor-temperature-analysis}{%
\subsection{Sensor Temperature
Analysis}\label{sensor-temperature-analysis}}

Compared to the \emph{MMC5603NJ}, the temperature plot of the
\emph{TLV493D} shows that the internal temperature sensor is very noisy
(maximum of \(\sigma^2_{t}\)=\emph{2\(^{\circ}\)C})and deviates from the
ambient temperature at almost \emph{10\(^{\circ}\)C}. With a further
measurement run with a different temperature setting of
\emph{30\(^{\circ}\)C}, the offset is reduced to only
\emph{4\(^{\circ}\)C} to the set temperature. However, the noise remains
constant. When using an alternative sensor, this behaviour is reflected
and therefore the internal temperature sensor of the \emph{TLV493D}
should not be used for subsequent temperature compensation.

\hypertarget{raw-sensor-data-analysis}{%
\subsection{Raw Sensor Data Analysis}\label{raw-sensor-data-analysis}}

\hypertarget{noise-level-data-analysis}{%
\subsection{Noise Level Data Analysis}\label{noise-level-data-analysis}}

@@

\hypertarget{temperature-sensitivity}{%
\section{Temperature Sensitivity}\label{temperature-sensitivity}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
\caption{Sensor temperature sensitivity evaluation results for TLV493D
and MMC5603NJ
\label{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}}
\end{figure}

using same setup as in read noise but with programmed temperature
controller of the chamber and separate temperature probe under the
sensors pcb

\hypertarget{linearity}{%
\section{Linearity}\label{linearity}}

@@

\hypertarget{result-analysis-1}{%
\section{Result Analysis}\label{result-analysis-1}}

@@

\hypertarget{recommendation-for-action}{%
\subsection{recommendation for action}\label{recommendation-for-action}}

\begin{itemize}
\tightlist
\item
  folgendes setup woird für eine vermessung nach der sensor auswertung
  emholen:
\item
  temperaturkomensation sowie linearitäts kompensation mit separaten
  temperatur sensor
\end{itemize}
